Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-05-17 supp_mat_complexity_selection.Rmd
working draft of code for analysis is finished.

Load dataset. This dataset is a subset that only includes larva that survive to pupation or turned into parasitoids. We omitted any data where larva mortality was unclear. This enabled us to focus on the selection pressures imposed by insect parasitoids rather than other sources.
```{r Preliminaries, message=FALSE, warning=FALSE, include=FALSE}
## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
library(tidyverse)
library(cowplot) # pretty default ggplots
library(broom) # for tidying multiple linear models
library(mgcv) # generalized additive models
library(gamm4) # generalized additive mixed-models
library(gsg) # calculating selection gradients
library(visreg)
library(viridis) # for color palette

@@

## CREATE SEPARATE DATASETS FOR SELECTION ANALYSES ----
control_df <- gall_selection.df %>%
  filter(Treatment.focus == "Control") %>%
  mutate(c.Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
         c.gall_individuals = gall_individuals - mean(gall_individuals),
         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))

treatment_df <- gall_selection.df %>%
  filter(Treatment.focus == "Ectoparasitoid exclusion") %>%
  mutate(c.Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
         c.gall_individuals = gall_individuals - mean(gall_individuals),
         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
```

```{r FUNCTIONS}
gamm.model <- function(formula, data) {
  gamm4(formula, data, 
        random = ~(1|Plant_Position/Gall_Number), # Genotype/
        family = binomial(link = logit))
}

@@

# experimenting with boot.case gave bootstrapped distributions that weren't centered near the model mean estimate.
# also, using 'refit.smooth = T' also generated some very skewed distributions
# the recipe below provided the most sensible estimates for my data
gradient.calc <- function(mod, phenotype, covariates = NULL) {
  gam.gradients(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32, 
                refit.smooth = F, 
                n.boot = 1000,
                se.method = 'boot.para',
                standardized = T)
}

@@

get_insect_FL.df <- function(FL){
  data.frame(mean_fitness = FL$Wbar, FL$points, t(FL$WbarPI)) %>%
    mutate(lower_2.5 = X2.5., upper_97.5 = X97.5.)
}

ggplot_uniFL <- function(FL.df) {
  ggplot(FL.df, aes(x = Var1, y = mean_fitness)) +
    geom_line() + 
    geom_ribbon(aes(ymin = lower_2.5, ymax = upper_97.5), alpha = 0.5)
}
```

@@

## CONTROL PLANTS ----
gamm_full.control <- gamm.model(gall_survival ~ 
                                  s(c.Gall_Height_mm) + 
                                  s(c.gall_individuals, k=9) + 
                                  s(c.Density_per_100_shoots) +
                                  c.Gall_Height_mm:c.gall_individuals + 
                                  c.Gall_Height_mm:c.Density_per_100_shoots + 
                                  c.gall_individuals:c.Density_per_100_shoots,
                                data = control_df)
summary(gamm_full.control$gam)
summary(gamm_full.control$mer)

gamm_red.control <- gamm.model(gall_survival ~ 
                                  s(c.Gall_Height_mm) + 
                                  s(c.gall_individuals, k=9) + 
                                  s(c.Density_per_100_shoots),
                                data = control_df)
summary(gamm_red.control$gam)
summary(gamm_red.control$mer)

@@

## TREATMENT PLANTS ----
gamm_full.treatment <- gamm.model(gall_survival ~ 
                                  s(c.Gall_Height_mm) + 
                                  s(c.gall_individuals, k=9) + 
                                  s(c.Density_per_100_shoots) +
                                  c.Gall_Height_mm:c.gall_individuals + 
                                  c.Gall_Height_mm:c.Density_per_100_shoots + 
                                  c.gall_individuals:c.Density_per_100_shoots,
                                data = treatment_df)
summary(gamm_full.treatment$gam)
summary(gamm_full.treatment$mer)

gamm_red.treatment <- gamm.model(gall_survival ~ 
                                  s(c.Gall_Height_mm) + 
                                  s(c.gall_individuals, k=9) + 
                                  s(c.Density_per_100_shoots),
                                data = treatment_df)
summary(gamm_red.treatment$gam)
summary(gamm_red.treatment$mer)

AIC(gamm_full.treatment$mer, gamm_red.treatment$mer)
```

```{r SELECTION GRADIENTS}

## GALL SIZE ----
sg.size_control <- gradient.calc(mod = gamm_red.control$gam, 
                                 phenotype = "c.Gall_Height_mm", 
                                 covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
sg.size_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                   phenotype = "c.Gall_Height_mm", 
                                   covariates = c("c.gall_individuals","c.Density_per_100_shoots"))

## GALL INDIVIDUALS ----
sg.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                        phenotype = "c.gall_individuals", 
                                        covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
sg.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                          phenotype = "c.gall_individuals", 
                                          covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))

## GALL DENSITY ----
sg.density_control <- gradient.calc(mod = gamm_red.control$gam, 
                                    phenotype = "c.Density_per_100_shoots", 
                                    covariates = c("c.gall_individuals","c.Gall_Height_mm"))
sg.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                      phenotype = "c.Density_per_100_shoots", 
                                      covariates = c("c.gall_individuals","c.Gall_Height_mm"))

## PRINT TABLE ----
rbind(
  mutate(sg.size_control$ests, Food_Web_Treatment = "Complex"),
  mutate(sg.size_treatment$ests, Food_Web_Treatment = "Simple"),
  mutate(sg.individuals_control$ests, Food_Web_Treatment = "Complex"),
  mutate(sg.individuals_treatment$ests, Food_Web_Treatment = "Simple"),
  mutate(sg.density_control$ests, Food_Web_Treatment = "Complex"),
  mutate(sg.density_treatment$ests, Food_Web_Treatment = "Simple")
)

round(rbind(
  sg.size_control$ests,
  sg.size_treatment$ests,
  sg.individuals_control$ests,
  sg.individuals_treatment$ests,
  sg.density_control$ests,
  sg.density_treatment$ests
),3)

## BOOTSTRAPPED INTERVALS ----
bootstrap_df <- bind_rows(
  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Simple")
)

bootstrap_df %>%
  ggplot(., aes(x=Phenotype, y=Bootstrap_Estimates, fill=Food_Web_Treatment)) +
  geom_boxplot() +
  geom_hline(yintercept=0, linetype="dotted") +
  facet_wrap(~Selection_Type) +
  coord_flip() 
```

```{r}
sg.size.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                               phenotype = c("c.Gall_Height_mm", "c.gall_individuals"),
                                               covariates = c("c.Density_per_100_shoots"))
sg.size.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                                 phenotype = c("c.Gall_Height_mm", "c.gall_individuals"),
                                                 covariates = c("c.Density_per_100_shoots"))
sg.size.x.density_control <- gradient.calc(mod = gamm_red.control$gam, 
                                               phenotype = c("c.Gall_Height_mm", "c.Density_per_100_shoots"),
                                               covariates = c("c.gall_individuals"))
sg.size.x.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                                 phenotype = c("c.Gall_Height_mm","c.Density_per_100_shoots"),
                                                 covariates = c("c.gall_individuals"))
sg.density.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                                  phenotype = c("c.Density_per_100_shoots", "c.gall_individuals"),
                                                  covariates = c("c.Gall_Height_mm"))
sg.density.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                                    phenotype = c("c.Density_per_100_shoots", "c.gall_individuals"),
                                                    covariates = c("c.Gall_Height_mm"))

# note that while the means are always the same for each gradient calculation, the SE and p-values can be slightly different. I always reported the highest SE and highest P-value to be conservative
bind_rows(data.frame(round(sg.size.x.individuals_control$ests,3), 
                     gradients = rownames(sg.size.x.individuals_control$ests),
                     treatment = "Complex"),
          data.frame(round(sg.size.x.individuals_treatment$ests,3), 
                     gradients = rownames(sg.size.x.individuals_treatment$ests),
                     treatment = "Simple"),
          data.frame(round(sg.size.x.density_control$ests,3), 
                     gradients = rownames(sg.size.x.density_control$ests),
                     treatment = "Complex"),
          data.frame(round(sg.size.x.density_treatment$ests,3), 
                     gradients = rownames(sg.size.x.density_treatment$ests),
                     treatment = "Simple"),
          data.frame(round(sg.density.x.individuals_control$ests,3), 
                     gradients = rownames(sg.density.x.individuals_control$ests),
                     treatment = "Complex"),
          data.frame(round(sg.density.x.individuals_treatment$ests,3), 
                     gradients = rownames(sg.density.x.individuals_treatment$ests),
                     treatment = "Simple")) %>%
  distinct %>%
  arrange(gradients)

```

@@

## GALL SIZE
fl.size_control <- insect_FL(mod = gamm_red.control$gam, 
                                 phenotype = "c.Gall_Height_mm", 
                                 covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
fl.size_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                   phenotype = "c.Gall_Height_mm", 
                                   covariates = c("c.gall_individuals","c.Density_per_100_shoots"))

## GALL INDIVIDUALS
fl.individuals_control <- insect_FL(mod = gamm_red.control$gam, 
                                        phenotype = "c.gall_individuals", 
                                        covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
fl.individuals_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                          phenotype = "c.gall_individuals", 
                                          covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))

## GALL DENSITY 
fl.density_control <- insect_FL(mod = gamm_red.control$gam, 
                                    phenotype = "c.Density_per_100_shoots", 
                                    covariates = c("c.gall_individuals","c.Gall_Height_mm"))
fl.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                      phenotype = "c.Density_per_100_shoots", 
                                      covariates = c("c.gall_individuals","c.Gall_Height_mm"))

## GALL INDIVIDUALS X DENSITY
fl.individuals.x.density_control <- insect_FL(mod = gamm_red.control$gam, 
                                              phenotype = c("c.Density_per_100_shoots","c.gall_individuals"), 
                                              covariates = c("c.Gall_Height_mm"))
fl.individuals.x.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                                phenotype = c("c.Density_per_100_shoots","c.gall_individuals"), 
                                                covariates = c("c.Gall_Height_mm"))

## GALL INDIVIDUALS x SIZE
fl.individuals.x.size_control <- insect_FL(mod = gamm_red.control$gam, 
                                            phenotype = c("c.Gall_Height_mm","c.gall_individuals"), 
                                            covariates = c("c.Density_per_100_shoots"))
fl.individuals.x.size_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                             phenotype = c("c.Gall_Height_mm","c.gall_individuals"), 
                                             covariates = c("c.Density_per_100_shoots"))

## GALL DENSITY X SIZE
fl.size.x.density_control <- insect_FL(mod = gamm_red.control$gam, 
                                       phenotype = c("c.Density_per_100_shoots","c.Gall_Height_mm"), 
                                       covariates = c("c.gall_individuals"))
fl.size.x.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                         phenotype = c("c.Density_per_100_shoots","c.Gall_Height_mm"), 
                                         covariates = c("c.gall_individuals"))

@@

uni_plots <- plot_grid(uni_size + theme(legend.position = "none"), 
                       uni_clutch + theme(legend.position = "none", 
                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
                       uni_pref + theme(legend.position = "none", 
                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
                       labels = "AUTO", nrow = 1, align='hv')
plot_grid(uni_plots, uni_legend, ncol=2, rel_widths = c(3,0.3))

## 2-DIMENSIONAL

bind_rows(mutate(get_insect_FL.df(fl.individuals.x.density_treatment), Treatment="Simple"),
          mutate(get_insect_FL.df(fl.individuals.x.density_control), Treatment="Complex")) %>%
  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
  geom_raster() + 
  facet_wrap(~Treatment) +
  scale_fill_viridis() +
  xlab("Female preference") +
  ylab("Clutch size")

bind_rows(mutate(get_insect_FL.df(fl.individuals.x.size_treatment), Treatment="Simple"),
          mutate(get_insect_FL.df(fl.individuals.x.size_control), Treatment="Complex")) %>%
  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
  geom_raster() + 
  facet_wrap(~Treatment) +
  scale_fill_viridis() +
  xlab("Clutch size") +
  ylab("Gall size")

bind_rows(mutate(get_insect_FL.df(fl.size.x.density_treatment), Treatment="Simple"),
          mutate(get_insect_FL.df(fl.size.x.density_control), Treatment="Complex")) %>%
  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
  geom_raster() + 
  facet_wrap(~Treatment) +
  scale_fill_viridis() +
  xlab("Gall size") +
  ylab("Female preference")
```

>>>>

Load dataset. This dataset is a subset that only includes larva that survive to pupation or turned into parasitoids. We omitted any data where larva mortality was unclear. This enabled us to focus on the selection pressures imposed by insect parasitoids rather than other sources.
```{r Preliminaries, message=FALSE, warning=FALSE, include=FALSE}

## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
library(tidyverse)
library(cowplot) # pretty default ggplots
library(broom) # for tidying multiple linear models
library(mgcv) # generalized additive models
library(gamm4) # generalized additive mixed-models
library(gsg) # calculating selection gradients
library(visreg)
library(viridis) # for color palette

@@

## CREATE SEPARATE DATASETS FOR SELECTION ANALYSES ----
control_df <- gall_selection.df %>%
  filter(Treatment.focus == "Control") %>%
  mutate(Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
         gall_individuals = gall_individuals - mean(gall_individuals),
         Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))

treatment_df <- gall_selection.df %>%
  filter(Treatment.focus == "Ectoparasitoid exclusion") %>%
  mutate(Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
         gall_individuals = gall_individuals - mean(gall_individuals),
         Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
```

```{r FUNCTIONS}
gamm.model <- function(formula, data) {
  gamm4(formula, data, 
        random = ~(1|Genotype/Plant_Position/Gall_Number), 
        family = binomial(link = logit))
}

@@

# experimenting with boot.case gave bootstrapped distributions that weren't centered near the model mean estimate.
# also, using 'refit.smooth = T' also generated some very skewed distributions
# the recipe below provided the most sensible estimates for my data
gradient.calc <- function(mod, phenotype, covariates = NULL) {
  gam.gradients(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32, 
                refit.smooth = T, # F
                n.boot = 1000,
                se.method = 'boot.para', #'posterior', #'boot.para', #'permute', 'boot.case'#  
                standardized = T)
}

@@

get_insect_FL.df <- function(FL){
  data.frame(mean_fitness = FL$Wbar, FL$points, t(FL$WbarPI)) %>%
    mutate(lower_2.5 = X2.5., upper_97.5 = X97.5.)
}
```

@@

## CONTROL PLANTS ----
gamm_full.control <- gamm.model(gall_survival ~ 
                                  s(Gall_Height_mm) + 
                                  s(gall_individuals, k=9) + 
                                  s(Density_per_100_shoots) +
                                  Gall_Height_mm:gall_individuals + 
                                  Gall_Height_mm:Density_per_100_shoots + 
                                  gall_individuals:Density_per_100_shoots,
                                data = control_df)
summary(gamm_full.control$gam)
summary(gamm_full.control$mer)

gamm_red.control <- gamm.model(gall_survival ~ 
                                  s(Gall_Height_mm) + 
                                  s(gall_individuals, k=9) + 
                                  s(Density_per_100_shoots),
                                data = control_df)
summary(gamm_red.control$gam)
summary(gamm_red.control$mer)

@@

## TREATMENT PLANTS ----
gamm_full.treatment <- gamm.model(gall_survival ~ 
                                  s(Gall_Height_mm) + 
                                  s(gall_individuals, k=9) + 
                                  s(Density_per_100_shoots) +
                                  Gall_Height_mm:gall_individuals + 
                                  Gall_Height_mm:Density_per_100_shoots + 
                                  gall_individuals:Density_per_100_shoots,
                                data = treatment_df)
summary(gamm_full.treatment$gam)
summary(gamm_full.treatment$mer)

gamm_red.treatment <- gamm.model(gall_survival ~ 
                                  s(Gall_Height_mm) + 
                                  s(gall_individuals, k=9) + 
                                  s(Density_per_100_shoots),
                                data = treatment_df)
summary(gamm_red.treatment$gam)
summary(gamm_red.treatment$mer)

AIC(gamm_full.treatment$mer, gamm_red.treatment$mer)
```
Parametric bootstrapping: Currently reported results

Case-wise bootstrapping: qualitative results match parametric bootstrapping.

Posterior: qualitative results match parametric bootstrapping, except that non-linear selection on gall size in the complex food-web is no longer significant.

Permutation: qualtiative results are consistent with parametric bootstrapping. Exceptions include: in the simple food-web, there is no evidence of non-linear selection for gall density or gall individuals. In the complex food-web, there is only marginal evidence for non-linear selection acting on gall size, but there is evidence for correlational selection between gall size and the number of individuals per gall.
```{r SELECTION GRADIENTS, echo=TRUE, warning=FALSE}
## Estimate directional, nonlinear, and correlational selection gradients
sg.size_control <- gradient.calc(mod = gamm_red.control$gam, 
                                 phenotype = "Gall_Height_mm", 
                                 covariates = c("gall_individuals","Density_per_100_shoots"))
sg.size_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                   phenotype = "Gall_Height_mm", 
                                   covariates = c("gall_individuals","Density_per_100_shoots"))
sg.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                        phenotype = "gall_individuals", 
                                        covariates = c("Gall_Height_mm","Density_per_100_shoots"))
sg.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                          phenotype = "gall_individuals", 
                                          covariates = c("Gall_Height_mm","Density_per_100_shoots"))
sg.density_control <- gradient.calc(mod = gamm_red.control$gam, 
                                    phenotype = "Density_per_100_shoots", 
                                    covariates = c("gall_individuals","Gall_Height_mm"))
sg.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                      phenotype = "Density_per_100_shoots", 
                                      covariates = c("gall_individuals","Gall_Height_mm"))
sg.size.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                               phenotype = c("Gall_Height_mm", "gall_individuals"),
                                               covariates = c("Density_per_100_shoots"))
sg.size.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                                 phenotype = c("Gall_Height_mm", "gall_individuals"),
                                                 covariates = c("Density_per_100_shoots"))
sg.size.x.density_control <- gradient.calc(mod = gamm_red.control$gam, 
                                               phenotype = c("Gall_Height_mm", "Density_per_100_shoots"),
                                               covariates = c("gall_individuals"))
sg.size.x.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                                 phenotype = c("Gall_Height_mm","Density_per_100_shoots"),
                                                 covariates = c("gall_individuals"))
sg.density.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                                  phenotype = c("Density_per_100_shoots", "gall_individuals"),
                                                  covariates = c("Gall_Height_mm"))
sg.density.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                                    phenotype = c("Density_per_100_shoots", "gall_individuals"),
                                                    covariates = c("Gall_Height_mm"))

## Summarise the results
sg.summary <- bind_rows(
          data.frame(sg.size_control$ests, #round(,3), 
                     gradients = rownames(sg.size_control$ests),
                     treatment = "Complex"),
          data.frame(sg.size_treatment$ests, #round(,3), 
                     gradients = rownames(sg.size_treatment$ests),
                     treatment = "Simple"),
          data.frame(sg.individuals_control$ests, #round(,3), 
                     gradients = rownames(sg.individuals_control$ests),
                     treatment = "Complex"),
          data.frame(sg.individuals_treatment$ests, #round(,3), 
                     gradients = rownames(sg.individuals_treatment$ests),
                     treatment = "Simple"),
          data.frame(sg.density_control$ests, #round(,3), 
                     gradients = rownames(sg.density_control$ests),
                     treatment = "Complex"),
          data.frame(sg.density_treatment$ests, #round(,3), 
                     gradients = rownames(sg.density_treatment$ests),
                     treatment = "Simple"),
          data.frame(sg.size.x.individuals_control$ests, #round(,3), 
                     gradients = rownames(sg.size.x.individuals_control$ests),
                     treatment = "Complex")[5,],
          data.frame(sg.size.x.individuals_treatment$ests, #round(,3), 
                     gradients = rownames(sg.size.x.individuals_treatment$ests),
                     treatment = "Simple")[5,],
          data.frame(sg.size.x.density_control$ests, #round(,3), 
                     gradients = rownames(sg.size.x.density_control$ests),
                     treatment = "Complex")[5,],
          data.frame(sg.size.x.density_treatment$ests, #round(,3), 
                     gradients = rownames(sg.size.x.density_treatment$ests),
                     treatment = "Simple")[5,],
          data.frame(sg.density.x.individuals_control$ests, #round(,3), 
                     gradients = rownames(sg.density.x.individuals_control$ests),
                     treatment = "Complex")[5,],
          data.frame(sg.density.x.individuals_treatment$ests, #round(,3), 
                     gradients = rownames(sg.density.x.individuals_treatment$ests),
                     treatment = "Simple")[5,])

## Table of Estimates
sg.table <- sg.summary %>%
  mutate(plus_minus = "\u00B1", estimates = round(estimates, 4), SE = round(SE, 4)) %>%
  unite(col = estimate_SE, from = c("estimates", "plus_minus", "SE"), sep="") %>%
  select(-P.value) %>%
  spread(treatment, estimate_SE)
sg.table
write_csv(sg.table, "sg.table.csv")

## Table of P-values
sg.summary %>%
  select(-estimates, -SE) %>%
  spread(treatment, P.value)
```

```{r}
hist(as.numeric(sg.density_control$boot[ ,1]))
## BOOTSTRAPPED INTERVALS ----
bootstrap_df <- bind_rows(
  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = as.numeric(sg.density_control$boot[ ,1]), Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = as.numeric(sg.density_control$boot[ ,2]), Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  # correlational
  data.frame(Bootstrap_Estimates = as.numeric(sg.size.x.individuals_control$boot[ ,5]), Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size.x.individuals_treatment$boot[ ,5], Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
    data.frame(Bootstrap_Estimates = sg.size.x.density_control$boot[ ,5], Phenotype = "Size,Preference", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size.x.density_treatment$boot[ ,5], Phenotype = "Size,Preference", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.density.x.individuals_control$boot[ ,5], Phenotype = "Preference,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.density.x.individuals_treatment$boot[ ,5], Phenotype = "Preference,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple")
)

bootstrap_df %>%
  #filter(Selection_Type == "Gamma") %>%
  ggplot(., aes(x=Phenotype, y=Bootstrap_Estimates, fill=Food_Web_Treatment)) +
  geom_boxplot() +
  geom_hline(yintercept=0, linetype="dotted") +
  facet_wrap(~Selection_Type, scales = "free_x") +
  coord_flip() 
```

@@

## GALL SIZE
fl.size_control <- insect_FL(mod = gamm_red.control$gam, 
                                 phenotype = "Gall_Height_mm", 
                                 covariates = c("gall_individuals","Density_per_100_shoots"))
fl.size_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                   phenotype = "Gall_Height_mm", 
                                   covariates = c("gall_individuals","Density_per_100_shoots"))

## GALL INDIVIDUALS
fl.individuals_control <- insect_FL(mod = gamm_red.control$gam, 
                                        phenotype = "gall_individuals", 
                                        covariates = c("Gall_Height_mm","Density_per_100_shoots"))
fl.individuals_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                          phenotype = "gall_individuals", 
                                          covariates = c("Gall_Height_mm","Density_per_100_shoots"))

## GALL DENSITY 
fl.density_control <- insect_FL(mod = gamm_red.control$gam, 
                                    phenotype = "Density_per_100_shoots", 
                                    covariates = c("gall_individuals","Gall_Height_mm"))
fl.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                      phenotype = "Density_per_100_shoots", 
                                      covariates = c("gall_individuals","Gall_Height_mm"))

## GALL INDIVIDUALS X DENSITY
fl.individuals.x.density_control <- insect_FL(mod = gamm_red.control$gam, 
                                              phenotype = c("Density_per_100_shoots","gall_individuals"), 
                                              covariates = c("Gall_Height_mm"))
fl.individuals.x.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                                phenotype = c("Density_per_100_shoots","gall_individuals"), 
                                                covariates = c("Gall_Height_mm"))

## GALL INDIVIDUALS x SIZE
fl.individuals.x.size_control <- insect_FL(mod = gamm_red.control$gam, 
                                            phenotype = c("Gall_Height_mm","gall_individuals"), 
                                            covariates = c("Density_per_100_shoots"))
fl.individuals.x.size_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                             phenotype = c("Gall_Height_mm","gall_individuals"), 
                                             covariates = c("Density_per_100_shoots"))

## GALL DENSITY X SIZE
fl.size.x.density_control <- insect_FL(mod = gamm_red.control$gam, 
                                       phenotype = c("Density_per_100_shoots","Gall_Height_mm"), 
                                       covariates = c("gall_individuals"))
fl.size.x.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                         phenotype = c("Density_per_100_shoots","Gall_Height_mm"), 
                                         covariates = c("gall_individuals"))

@@

uni_plots <- plot_grid(uni_size + theme(legend.position = "none"), 
                       uni_clutch + theme(legend.position = "none", 
                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
                       uni_pref + theme(legend.position = "none", 
                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
                       labels = "AUTO", ncol = 4, align='hv')

fitness_landscapes_1d <- ggdraw(uni_plots) + draw_grob(uni_legend, x = 0.8, y=0) #plot_grid(uni_plots, uni_legend, ncol=2, rel_widths = c(3,0.3))
fitness_landscapes_1d
save_plot("fitness_landscapes_1d.png", fitness_landscapes_1d, base_height=6, base_width = 8)

## 2-DIMENSIONAL
clutch.x.size_2d <- bind_rows(
  mutate(get_insect_FL.df(fl.individuals.x.size_treatment), Treatment="Simple"),
  mutate(get_insect_FL.df(fl.individuals.x.size_control), Treatment="Complex")) %>%
  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
  geom_raster() + 
  facet_wrap(~Treatment) +
  scale_fill_viridis(name = "Mean fitness") +
  xlab("Mean gall size") +
  ylab("Mean clutch size")

size.x.pref_2d <- bind_rows(
  mutate(get_insect_FL.df(fl.size.x.density_treatment), Treatment="Simple"),
  mutate(get_insect_FL.df(fl.size.x.density_control), Treatment="Complex")) %>%
  ggplot(., aes(x=Var2, y=Var1, fill=mean_fitness)) +
  geom_raster() + 
  facet_wrap(~Treatment) +
  scale_fill_viridis(name = "Mean fitness") +
  xlab("Mean gall size") +
  ylab("Mean female preference")

clutch.x.pref_2d <- bind_rows(
  mutate(get_insect_FL.df(fl.individuals.x.density_treatment), Treatment="Simple"),
  mutate(get_insect_FL.df(fl.individuals.x.density_control), Treatment="Complex")) %>%
  ggplot(., aes(x=Var2, y=Var1, fill=mean_fitness)) +
  geom_raster() + 
  facet_wrap(~Treatment) +
  scale_fill_viridis(name = "Mean fitness") +
  xlab("Mean clutch size") +
  ylab("Mean female preference")

legend_2d <- get_legend(clutch.x.size_2d)
